Efficient toolkit implementing best practices for principal component analysis of population genetic data

### 2019-10-21 paper-bedpca.tex
save

@@

@@

%[SEPARATE STEPS?]

@@

To show that we provide very performant implementations of the different methods presented in this paper, we apply them to the UK Biobank. We use 20 physical cores for most of the computations.
It takes 22 minutes to perform a first phase of clumping on 488,371 individuals genotyped over 504,139 variants, which reduces the number of variants to 261,307. It then takes 34 minutes to compute the first 20 PCs using these 261,307 variants.
If performing the automatic procedure for LD detection, it takes 5 hours to perform the initial clumping step, 6 computation of PCs and 5 outlier variant detection (i.e.\ 5 iterations of outlier detection and one final computation of PCs).

@@

@@

>>>>

[FIGURE TO ILLUSTRATE THIS?]

@@

[SHOULD DESCRIBE QC FOR OTHER DATASETS TOO?]

@@

[SCHEME TO ILLUSTRATE OADP?]

@@

To show that we provide very performant implementations of the different methods presented in this paper, we apply them to the UK Biobank. We use 20 physical cores for most of the computations.
It takes 22 minutes to perform a first phase of clumping on 406,545 unrelated individuals genotyped over 504,139 variants, which reduces the number of variants to 261,307. It then takes 34 minutes to compute the first 20 PCs using these 261,307 variants.
If performing the automatic procedure for LD detection, it takes 5 hours to perform the initial clumping step, 6 computation of PCs and 5 outlier variant detection (i.e.\ 5 iterations of outlier detection and one final computation of PCs).

@@

Finally, it took only 6 minutes to compute the 30-Nearest Neighbours of PC scores for all UK Biobank individuals.

@@

\noindent[SHOW THAT PROCEDURE IS OKAY FOR SMALLER DATASETS?]
